\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.92]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{2.5cm} % Uncomment to change the width of the dates column
\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\firstname{Daniel}
\familyname{Nieters}

\title{Systems Security Engineer}
\address{6265 Cates Ave. Apt. 2W}{Saint Louis, MO 63130}
\mobile{314.650.7102}
\phone{314.640.9154}
\email{dnieters@gmail.com}
\homepage{github.com/drnr53}{github.com/drnr53}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2008--2010}{Master of Science, Information Science \& Technology}{Missouri S\&T}{GPA: 3.5}{}{Certificate in Computer Engineering -- Information Assurance \& Security Officer Essentials}
\cventry{2005--2008}{Bachelor of Science, Information Science \& Technology}{Missouri S\&T}{GPA: 3.8}{}{Minor in Business Administration}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Work Experience}

\cventry{2013--Now}{Computing Security & Information Protection Specialist III}{The Boeing Company}{St. Louis, MO}{}{Technical lead on the information assurance implementation for the U.S. Navy's net-centric F/A-18 Automated Maintenance Environment (FAME). Maintained  IA controls to meet accreditation standards on over 3,000 hosts and 100 servers in squadrons across North America.
\begin{itemize}
\item Fully configured a lab environment for use in testing IA releases for the immediate IA team of 6 members, as well as all software QA testers. Environment contains dev and test versions of all production servers.
\item Administered and maintained rulesets, schedulers, and whitelists for host intrusion prevention systems, asset baseline monitoring, rogue host detection, and virus scanning using McAfee ePolicy Orchestrator.
\end{itemize}}

\cventry{2012--2013}{Security Engineer II}{The Boeing Company}{St. Louis, MO}{}{Technical lead on the information assurance implementation for the U.S. Navy's net-centric F/A-18 Automated Maintenance Environment (FAME). Maintained  IA controls to meet accreditation standards on over 3,000 hosts and 100 servers in squadrons across North America.
\begin{itemize}
\item Fully configured a lab environment for use in testing IA releases for the immediate IA team of 6 members, as well as all software QA testers. Environment contains dev and test versions of all production servers.
\item Administered and maintained rulesets, schedulers, and whitelists for host intrusion prevention systems, asset baseline monitoring, rogue host detection, and virus scanning using McAfee ePolicy Orchestrator.
\item Wrote IA lockdowns using C\# and batch scripting and coordinated their release through remote patching and physical software packages. Documented field security posture by configuring scan jobs using Nessus.
\item Compiled quarterly Certification and Accreditation packages for Navy customer utilizing OS patch and configuration vulnerability scanning. Wrote mitigation plans for zero-days and problematic lockdowns.
\end{itemize}}

\cventry{2010--2012}{Programmer/Analyst I}{The Boeing Company}{St. Louis, MO}{}{Application security assessment lead for the Application Consolidation \& Modernization team. Responsible for assessing risk, scanning, and advising mitigation strategies on over 500 internal applications at Boeing.
\begin{itemize}
\item Devised a risk assessment matrix to qualitatively assign risk to an application based on a list of criteria.
\item Utilized static code analysis and penetration testing tools to detail code-level vulnerabilities in applications containing HTML/Coldfusion, SQL, Java, etc.
\item Wrote reports detailing code remediation strategies and consulted with the individual developers.
\end{itemize}}

\cventry{2008--2009}{Student Programmer}{U.S. Geological Survey}{Rolla, MO}{}{Web developer for the National Geospatial Technical Operations Center
\begin{itemize}
\item Increased National Map functionality by integrating Google KML support and writing additional servlets. 
\item Supported 4 local machines serving Oracle, Mapserver, and Subversion  to centralize work within the team.
\end{itemize}}
 
%----------------------------------------------------------------------------------------
%	PROJECTS & INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Projects \& Interests}

\cvitem{Research}{Simulation of a Distributed and Transparent Firewall and Vulnerability Scanning System using OPNET}
\cvitem{Personal}{ArchReactor hackerspace (Member), Arduino, personal Web site, homebrewing, music}

%----------------------------------------------------------------------------------------
%	SOFTWARE SECTION
%----------------------------------------------------------------------------------------

\section{Language Experience}

\cvitem{Familiar}{C/C++, Javascript, Python, \LaTeX}
\cvitem{Proficient}{Java, HTML, SQL, Win/UNIX shell}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Software Experience}
\cvitem{OS}{Windows XP/7/2003/2008 Server, UNIX/Linux, Cisco IOS}
\cvitem{Programs}{VMWare ESXi, McAfee ePolicy Orchestrator, Tenable Nessus, SecurityCenter, nmap, Wireshark, IBM AppScan, Microsoft Visual Studio 2010}
 

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Certifications \& Awards}

\cvitem{Vocational}{CCNA, Security+, 6$\sigma$ Green Belt, DoD Secret Clearance}
\cvitem{Other}{Eagle Scout}

\end{document}
